### 2020-12-06 doc/manuscript/Dow_manuscript.Rmd
bot of work on methods/ results

The period where the phenology milestone(s) were most affected by changes in early spring temperature was determined using the R package *climwin* [@van_de_pol_identifying_2016]. 
This package tests the correlation between one or more climate variables and a biological variable over all consecutive time windows within a specified time-frame, reporting correlation and \$Delta AIC$ of each window. 
Here, we tested for correlation between temperature ($T_{max}$, $T_{min}$) and $DOY_{25}$ over the time window from February 1 (Julian day = 32) and the mean $DOY_{25}$ for the species group and site (Table `r mean_growth_parameters_table`).
*The critical time window is determined based on the subset of models that fall within the 95% confidence set.*
Here, we focused on defining critical temperature windows for $DOY_{25}$, as opposed to other growth phenology parameters (Figure `r schematic`), because we were interested in the influence of temperature on the initiation of woody growth. 
We note that other growth parameters would be controlled by different critical temperature windows; for example, at SCBI $\Delta DBH$ responds most strongly to May-July climate [@helcoski_growing_2019]. Determining the climate variables that most strongly control all parameters is beyond the scope of this analysis.

@@

For the majority of weekly time windows from Jan. 1 to $DOY_{25}$, there was neutral negative relationship between temperature and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (Figs. `r climwin`, `r all_climwin_SI_figs`). 
This held true for both ring- and diffuse-porous trees at both sites. 
The strongest relationships, including but not limited to the optimal time windows (Table `r mean_growth_parameters_table`), occurred for time windows closing $\le$ 5 weeks prior to $DOY_{25}$. 
(In general, there were significant negative relationships between temperature and $DOY_{25}$ for any time period beginning $\ge$ **5** weeks prior to $DOY_{25}$, ending  $\le$ **8-20** weeks prior depending on wood-type and site, and covering at least a **3**-week period (`r all_climwin_SI_figs`).
Relationships tended to be weaker and more stochastic in sign for short time periods, particularly those just prior to $DOY_{25}$.)
(**Cameron, I'm not sure if the above text is up-to-date... Also, see [issue 34](https://github.com/EcoClimLab/growth_phenology/issues/34)** )

@@

>>>>

The period where the phenology milestone(s) were most affected by changes in early spring temperature was determined using the R package *climwin* [@van_de_pol_identifying_2016]. 
This package tests the correlation between one or more climate variables and a biological variable over all consecutive time windows within a specified time-frame, reporting correlation and \$Delta AIC$ of each window. 
Here, we tested for correlation between temperature ($T_{max}$, $T_{min}$) and $DOY_{25}$ over the time window from January 1 to the mean $DOY_{25}$ for the species group and site (Table `r mean_growth_parameters_table`).
*The critical time window is determined based on the subset of models that fall within the 95% confidence set.*
Here, we focused on defining critical temperature windows for $DOY_{25}$, as opposed to other growth phenology parameters (Figure `r schematic`), because we were interested in the influence of temperature on the initiation of woody growth. 
We note that other growth parameters would be controlled by different critical temperature windows; for example, at SCBI $\Delta DBH$ responds most strongly to May-July climate [@helcoski_growing_2019]. Determining the climate variables that most strongly control all parameters is beyond the scope of this analysis.

@@

For the majority of weekly time windows from Jan. 1 to $DOY_{25}$, there was a negative or neutral relationship between $T_{max}$ and $DOY_{25}$, meaning that warmer temperatures shifted growth earlier in the season (Figs. `r climwin`, `r all_climwin_SI_figs`). 
This held true for both ring- and diffuse-porous trees at both sites. 
The strongest relationships, including but not limited to the optimal time windows (Table `r mean_growth_parameters_table`), occurred for time windows closing $\le$ 5 weeks prior to $DOY_{25}$. 
(In general, there were significant negative relationships between temperature and $DOY_{25}$ for any time period beginning $\ge$ **5** weeks prior to $DOY_{25}$, ending  $\le$ **8-20** weeks prior depending on wood-type and site, and covering at least a **3**-week period (`r all_climwin_SI_figs`).
Relationships tended to be weaker and more stochastic in sign for short time periods, particularly those just prior to $DOY_{25}$.)
(**Cameron, I'm not sure if the above text is up-to-date... ** )

@@

*$DOY_{25}$ was generally less strongly correlated with $T_{min}$ than with $T_{max}$.-- not sure this is true*
(*give some details, cite SI tables.*)

Henceforth, we focus on $T_{max}$.
